Generic Properties of D-optimal Designs in Infinite Dimensional Bayesian Linear Inverse Problems

### 2023-04-08 latex/intro.tex
Almost done?

It seems counter intuitive that when one computes an optimal design
using the D-optimality criterion, the optimization process results in
observations that are very similar. For example, if an observation is
thought of as measuring some function value at $\x \in \Omega
\subseteq \R^d, d=1,2,3$ (with added error) then the optimization
procedure sometimes places sensors in very close proximity to each
other (as can be seen in figure \ref{fig:clusterization
  illustration}). Following \cite{Ucinski05}, we refer to this
phenomenon as \emph{sensor clusterization}.

@@

\subsection{Contribution}
I propose and study a relaxed and analytically tractable model for
D-optimal designs. Under this model, D-optimal designs are solutions
of a constrained optimization problem, formulated using Lagrange
multipliers. This allows me to rigorously show how model error
mitigates clusterization (section \ref{section:non vanishing}). I show
that designs that exhibit clusterization are indeed optimal.

@@

When no model error is present, the Lagrange multipliers problem boils
down to a nonlinear eigenvalue problem.
%% The operator for which eigenvectors and eigenvalues are sought is a
%% sum of two operators. The first is the prior covariance. The second
%% is an outer product of the observations (see section
%% \ref{section:vanishing} for details and exact statement).
This structure helps me characterize D-optimal designs. The key idea
is that a D-optimal design reduces uncertainties where they are
highest first. This is the main conclusion of Theorem \ref{thm:char}
stated below.

\begin{restatable}[D-optimal designs with vanishing model error]{theorem}{char}\label{thm:char}
%% \begin{theorem}[D-optimal designs with vanishing model error]\label{thm:char}
  Let:
  \begin{itemize}
  \item $\hilp, \hilo$ Hilbert spaces.
  \item $\fwd:\hilp \to \hilo$ a linear compact operator.
  \item $\pr \sim \mathcal{N}(0, \prcov)$ prior Gaussian measure on $\hilp$,
    where $\prcov:\hilp \to \hilp$ is the prior covariance operator.
  \item $\obs: \hilo \to \mathbb{R}^m$ observation operator, where $m
    \in \mathbb{N}$ is the number of observations taken. 
  \item $\sigma^2 \in \mathbb{R}_{+}$ observation noise variance,
    $\data = \obs \fwd \param + \eps$, where $\eps \in \mathbb{R}^m$
    is iid $\mathcal{N}(0, \sigma^2)$ noise.
  \item $\post$ the posterior measure, with covariance $\postcov$.
  \item A D-optimality utility function
    \cite{AlexanderianGloorGhattas14}:
    \begin{align*}
      \begin{split}
        \tar(\obs) :&= \mathbb{E}_{\data}\left [ D_{\text{KL}} (\post || \pr ) \right ] \\
        % 
        % 
        % 
        &= \frac12 \log \det ( I + \sigma^{-2} \prcov^{1/2} \fwd ^*
        \obs^* \obs \fwd \prcov^{1/2}).
      \end{split}
    \end{align*}
  \item $\{\lambda_i\}_{i=1}^\infty$ eigenvalues of $\fwd\prcov\fwd^*$
    in decreasing order of magnitude.
  %% \item $\{\ev_i\}_{i=1}^\infty$ their corresponding eigenvectors.
  \item $\{\eta_i\}_{i=1}^\infty$ eigenvalues of $\obs^*\obs$.
  \end{itemize}

  If $\obs$ is a D-optimal design operator
    \begin{equation*}
      \obs = \argmax_{\|\meas_j\| = 1, j=1,\dots,m}\tar(\obs), 
    \end{equation*}
    then:
  \begin{enumerate}
  \item  $\tr{\obs^*\obs} = m$.
  \item $\obs^*\obs$ and $\fwd\prcov\fwd^*$ are simultaneously
    diagonalizable.
  \item $k := \rank \obs^*\obs \leq m$ and
    \begin{equation*}
      \tar(\obs) = \frac12 \sum_{i=1}^{k} \log (1 + \sigma^{-2}\lambda_i\eta_i). %= \frac12 \sum_{i=1}^{m} \log (1 + \sigma^{-2}\lambda_i\eta_i).
    \end{equation*}
  %% \item 
  %%   \begin{equation*}
  %%     k = \argmax \left \{ k:\lambda_k^{-1} < \sigma^{-2}\frac{m}{k} + \frac{1}{k} \sum_{j=1}^{k}
  %%     \lambda_j^{-1} \right \}.
  %%   \end{equation*}
  \item
    \begin{equation*}
        \eta_i = \begin{cases}
          \frac{m}{k} - \sigma^2 \lambda_i^{-1} + \sigma^2 \frac{1}{k} \sum_{j=1}^k \lambda_j^{-1} & 1 \leq i \leq k \\
          0 & i > k 
        \end{cases}.
    \end{equation*}
  \item The covariance of the pushforwad $\fwd_{*} \post$ is $\left (
    (\fwd \prcov \fwd^*)^{-1} + \sigma^{-2} \obs^*\obs \right )^{-1}$
    and has eigenvalues
    \begin{equation*}
      \theta_i =
      \begin{cases}
        \left(\frac{\sum_{j=1}^k \lambda_j^{-1} + \sigma^{-2}m}{k} \right )^{-1} & i \leq k \\
        \lambda_i &  i > k 
      \end{cases}
    \end{equation*}
  \end{enumerate}
%\end{theorem}
\end{restatable}

@@

In the process, I generalize several lemmas from linear algebra to
infinite-dimensional settings. I prove a Matrix Determinant Lemma in
\ref{lemma:MDL}. I generalize a lemma due to Lax \cite{Lax07} for
calculating $\frac{\der}{\der t} \log \det (I + X(t))$, for an
operator valued function $X(t)$ in \ref{lemma:lax}. I show how to
decompose a symmetric positive definite matrix $m$ as $M = AA^t$,
where $A$ has unit norm columns in Lemma \ref{lemma:free}.

\subsection{Limitations}\label{subsec:limitations}
Two main drawbacks of the study presented here are: First, the relaxed
model does not consider any specific set of allowed
observations. Rather, I take observations in the unit ball in some
Hilbert space. This allows considerably less restrictive observations
than any real-life problem does. The second drawback is that I do not
show rigorously that clusterization necessarily occurs, I only show
that it is as reasonable as no clusterization.

@@

    \end{axis}
  \end{tikzpicture}
  \caption{The clusterization effect for the 1D heat equation
    described in section \ref{subsec:example}. Posterior pointwise
    standard deviations (lines) are plotted over the domain $[0,
      \pi]$, for varying numbers of sensors. Sensor locations
    (circles) were chosen to minimize (an expression analogous to) the
    determinant of the posterior covariance. The clusterization effect
    can be clearly seen for six sensors. Only four observation
    locations are used --- two pairs of sensors are so close they are
    indistinguishable.}
  \label{fig:clusterization illustration}
\end{figure}

In section \ref{section:prelim}, I present a more abstract and general
formulation of the inverse problem I consider. But, for the purpose of
illustration, I present clusterization via a toy model --- the 1D heat
equation in $[0,\pi]$ with a homogeneous Dirichlet boundary condition.

@@

The goal is to infer the initial condition $u_0$. For that purpose, we
measure $u$ at some set of locations $\x_j \in [0,\pi], j=1, \dots,m$
and a final time $T > 0$. We assume centered Gaussian observation
error, so we observe $v(\x_j,T) = u(\x_j,T) + \eps(\x_j)$ with
$\eps(\x_j) \sim \normal(0, \sigma^2)$ iid, $\sigma^2 > 0$. We model
the initial condition as $u_0 \sim \normal(0,\prcov)$, for $\prcov =
(-\Delta)^{-1}$ with a homogeneous Dirichlet boundary condition. It is
known \cite{Tarantola05} that for linear problems, with Gaussian prior
and error, the posterior is also Gaussian with a covariance that does
not depend on the observed data. The posterior covariance $\postcov$
has a closed form formula, even in infinite dimensions
\cite{Stuart10}. We denote by $\fwd$ the dynamics operator, so that
$u( \cdot,T) = \fwd u_0$, and the observation operator $\obs$ so that
$u(\x_j,T) = (\obs u)_j, j=1,\dots,m$. The posterior covariance is
known and depends only on $\prcov, \fwd, \obs$ and $\sigma^2$ (see
section \ref{section:prelim} and \eqref{eq:postcov} specifically).

We consider generalization of the information-theoretic design
criterion presented in the introduction to infinite dimensions
(section \ref{subsec:D optimal design} below). We choose
$\x_j,j=1,\dots,m$ to minimize (an expression analogous to) the
determinant of the posterior covariance operator. We will see later
how this corresponds to maximizing expected information gain.

The clusterization effect is illustrated in figure
\ref{fig:clusterization illustration}. Posterior pointwise standard
deviations are plotted over the domain $[0, \pi]$. Since the posterior
covariance does not depend on data, the plot has no reference to
actual data observed. The posterior covariance does, however, depend
on location of the observation taken. In figure
\ref{fig:clusterization illustration}, observation locations are
marked by circles. These were chosen to minimize (an expression
analogous to) the determinant of the posterior covariance. The
clusterization effect can be clearly seen for six sensors. It looks
like only four observations were taken. The reason is that two pairs
of sensors are so close they are indistinguishable.

>>>>

It seems counter intuitive that when one computes an optimal design
using the D-optimality criterion, the optimization process results in
observations that are very similar. For example, if an observation is
thought of as measuring some function value at $\x \in \Omega
\subseteq \R^d, d=1,2,3$ (with added error) then the optimization
procedure sometimes places sensors in very close proximity to each
other (as can be seen in Figure \ref{fig:clusterization
  illustration}). Following \cite{Ucinski05}, we refer to this
phenomenon as \emph{sensor clusterization}.

@@

\subsection{Contribution}
We propose and study a relaxed and analytically tractable model for
D-optimal designs. Under this model, D-optimal designs are solutions
of a constrained optimization problem, formulated using Lagrange
multipliers. This allows me to rigorously show how model error
mitigates clusterization (Section \ref{section:non vanishing}). We
show that designs that exhibit clusterization are indeed optimal.

@@

When no model error is present, the Lagrange multipliers problem boils
down to a nonlinear eigenvalue problem.
%% The operator for which eigenvectors and eigenvalues are sought is a
%% sum of two operators. The first is the prior covariance. The second
%% is an outer product of the observations (see section
%% \ref{section:vanishing} for details and exact statement).
This structure helps us to characterize D-optimal designs. The key
idea is that a D-optimal design reduces uncertainties where they are
highest first. This is the main conclusion of Theorem \ref{thm:char}
stated below.

\begin{restatable}[D-optimal designs with vanishing model error]{theorem}{char}\label{thm:char}
  %% \begin{theorem}[D-optimal designs with vanishing model error]\label{thm:char}
  %% Let Notation \ref{not:setup}. Further, let

  Let:
  \begin{itemize}
  \item $\hilp, \hilo$ Hilbert spaces.
  \item $\fwd:\hilp \to \hilo$ a linear compact operator.
  \item $\pr \sim \mathcal{N}(0, \prcov)$ prior Gaussian measure on $\hilp$,
    where $\prcov:\hilp \to \hilp$ is the prior covariance operator.
  \item $\obs: \hilo \to \mathbb{R}^m$ observation operator, where $m
    \in \mathbb{N}$ is the number of observations taken. 
  \item $\sigma^2 \in \mathbb{R}_{+}$ observation noise variance,
    $\data = \obs \fwd \param + \eps$, where $\eps \in \mathbb{R}^m$
    is iid $\mathcal{N}(0, \sigma^2)$ noise.
  \item $\post$ the posterior measure, with covariance $\postcov$.
  \item A D-optimality utility function
    \cite{AlexanderianGloorGhattas14}:
    \begin{align*}
      \begin{split}
        \tar(\obs) :&= \mathbb{E}_{\data}\left [ D_{\text{KL}} (\post || \pr ) \right ] \\
        % 
        % 
        % 
        &= \frac12 \log \det ( I + \sigma^{-2} \prcov^{1/2} \fwd ^*
        \obs^* \obs \fwd \prcov^{1/2}).
      \end{split}
    \end{align*}
  \item $\{\lambda_i\}_{i=1}^\infty$ eigenvalues of $\fwd\prcov\fwd^*$
    in decreasing order of magnitude.
  %% \item $\{\ev_i\}_{i=1}^\infty$ their corresponding eigenvectors.
  \item $\{\eta_i\}_{i=1}^\infty$ eigenvalues of $\obs^*\obs$.
  \item $\obs$ a D-optimal design operator
    \begin{equation*}
      \obs = \argmax_{\|\meas_j\| = 1, j=1,\dots,m}\tar(\obs).
    \end{equation*}
  \end{itemize}

  Then:
  \begin{enumerate}
  \item  $\tr{\obs^*\obs} = m$.
  \item $\obs^*\obs$ and $\fwd\prcov\fwd^*$ are simultaneously
    diagonalizable.
  \item $k := \rank \obs^*\obs \leq m$ and
    \begin{equation*}
      \tar(\obs) = \frac12 \sum_{i=1}^{k} \log (1 + \sigma^{-2}\lambda_i\eta_i). %= \frac12 \sum_{i=1}^{m} \log (1 + \sigma^{-2}\lambda_i\eta_i).
    \end{equation*}
  %% \item 
  %%   \begin{equation*}
  %%     k = \argmax \left \{ k:\lambda_k^{-1} < \sigma^{-2}\frac{m}{k} + \frac{1}{k} \sum_{j=1}^{k}
  %%     \lambda_j^{-1} \right \}.
  %%   \end{equation*}
  \item
    \begin{equation*}
        \eta_i = \begin{cases}
          \frac{m}{k} - \sigma^2 \lambda_i^{-1} + \sigma^2 \frac{1}{k} \sum_{j=1}^k \lambda_j^{-1} & 1 \leq i \leq k \\
          0 & i > k 
        \end{cases}.
    \end{equation*}
  \item The covariance of the pushforwad $\fwd_{*} \post$ is $\left (
    (\fwd \prcov \fwd^*)^{-1} + \sigma^{-2} \obs^*\obs \right )^{-1}$
    and has eigenvalues
    \begin{equation*}
      \theta_i =
      \begin{cases}
        \left(\frac{\sum_{j=1}^k \lambda_j^{-1} + \sigma^{-2}m}{k} \right )^{-1} & i \leq k \\
        \lambda_i &  i > k 
      \end{cases}
    \end{equation*}
  \end{enumerate}
%\end{theorem}
\end{restatable}

@@

In the process, We generalize several lemmas from linear algebra to
infinite-dimensional settings. We prove a Matrix Determinant Lemma in
\ref{lemma:MDL}. We generalize a lemma due to Lax \cite{Lax07} for
calculating $\frac{\der}{\der t} \log \det (I + X(t))$, for an
operator valued function $X(t)$ in \ref{lemma:lax}. We show how to
decompose a symmetric positive definite matrix $m$ as $M = AA^t$,
where $A$ has unit norm columns in Lemma \ref{lemma:free}.

\subsection{Limitations}\label{subsec:limitations}
Two main drawbacks of the study presented here are: First, the relaxed
model does not consider any specific set of allowed
observations. Rather, we take observations in the unit ball in some
Hilbert space. This allows considerably less restrictive observations
than any real-life problem does. The second drawback is that we do not
show rigorously that clusterization necessarily occurs, we only show
that it is as reasonable as no clusterization.

@@

    \end{axis}
  \end{tikzpicture}
  \caption{The clusterization effect for the 1D heat equation
    described in Section \ref{subsec:example}. Posterior pointwise
    standard deviations (lines) are plotted over the domain $[0,
      \pi]$, for varying numbers of sensors. Sensor locations
    (circles) were chosen to minimize (an expression analogous to) the
    determinant of the posterior covariance. The clusterization effect
    can be clearly seen for six sensors. Only four observation
    locations are used --- two pairs of sensors are so close they are
    indistinguishable.}
  \label{fig:clusterization illustration}
\end{figure}

In Section \ref{section:prelim}, we present a more abstract and general
formulation of the inverse problem we consider. But, for the purpose of
illustration, we present clusterization via a toy model --- the 1D heat
equation in $[0,\pi]$ with a homogeneous Dirichlet boundary condition.

@@

The goal is to infer the initial condition $u_0$. For that purpose, we
measure $u$ at some set of locations $\x_j \in [0,\pi], j=1, \dots,m$
and a final time $T > 0$. We assume centered Gaussian observation
error, so we observe $v(\x_j,T) = u(\x_j,T) + \eps(\x_j)$ with
$\eps(\x_j) \sim \normal(0, \sigma^2)$ iid, $\sigma^2 > 0$. We model
the initial condition as $u_0 \sim \normal(0,\prcov)$, for $\prcov =
(-\Delta)^{-1}$ with a homogeneous Dirichlet boundary condition. It is
known \cite{Tarantola05} that for linear problems, with Gaussian prior
and error, the posterior is also Gaussian with a covariance that does
not depend on the observed data. The posterior covariance $\postcov$
has a closed form formula, even in infinite dimensions
\cite{Stuart10}. We denote by $\fwd$ the dynamics operator, so that
$u( \cdot,T) = \fwd u_0$, and the observation operator $\obs$ so that
$u(\x_j,T) = (\obs u)_j, j=1,\dots,m$. The posterior covariance is
known and depends only on $\prcov, \fwd, \obs$ and $\sigma^2$ (see
Section \ref{section:prelim} and \eqref{eq:postcov} specifically).

We consider generalization of the information-theoretic design
criterion presented in the introduction to infinite dimensions
(Section \ref{subsec:D optimal design} below). We choose
$\x_j,j=1,\dots,m$ to minimize (an expression analogous to) the
determinant of the posterior covariance operator. We will see later
how this corresponds to maximizing expected information gain.

The clusterization effect is illustrated in Figure
\ref{fig:clusterization illustration}. Posterior pointwise standard
deviations are plotted over the domain $[0, \pi]$. Since the posterior
covariance does not depend on data, the plot has no reference to
actual data observed. The posterior covariance does, however, depend
on location of the observation taken. In Figure
\ref{fig:clusterization illustration}, observation locations are
marked by circles. These were chosen to minimize (an expression
analogous to) the determinant of the posterior covariance. The
clusterization effect can be clearly seen for six sensors. It looks
like only four observations were taken. The reason is that two pairs
of sensors are so close they are indistinguishable.

### 2023-04-08 latex/prelims.tex
Almost done?

\subsection{Overview}
In this section I will define notations that will be used throughout
the paper. The theoretical foundations for inverse problems over
function spaces can be found in \cite{Stuart10}. Most of the notations
are summarized in the conditions of Theorem \ref{thm:char}.

@@

\subsubsection{Error Terms}
Considering the sum of the error terms, it is easy to verify that
$\bar{\eps} := \obs \eps' + \eps \in \R^m$. It is a centered Gaussian
random vector and its covariance matrix is
\begin{align}\label{eq:Sigma}
  \begin{split}
    \Sigma(\obs) :&= \mathbb{E}[ (\obs \eps' + \eps)  (\obs \eps' + \eps)^t ] 
    % 
    % 
    = \obs \modcov \obs^* + \sigma^2I , 
  \end{split}
\end{align}
where
\begin{equation}\label{eq:modcov explained}
  [\obs \modcov \obs^*]_{ij} = e_i^t \obs \modcov \obs^* e_j = \meas_i (\modcov \meas_j),
\end{equation}
with $e_j \in \R^m$ the $j$th standard basis vector. The first
equality in \eqref{eq:modcov explained} holds by definition and the
second by \eqref{eq:obs*}. The explicit dependence on $\obs$ will be
mostly dropped for notational convenience, so $\Sigma(\obs) =
\Sigma$. Thus, for a fixed $\obs$ (i.e.\ a fixed set of observations)
we can equivalently write $\data = \obs \fwd \param + \bar{\eps}$ with
$\bar{\eps} \sim \normal(0,\Sigma)$. Taking $\modcov = 0$ is common
practice \cite{Tarantola05,Kaipio2006,Vogel02}. This reduces to
the case where we take iid observations. Then $\Sigma = \sigma^2I$ is
simply a scalar matrix that does not depend on $\obs$. Note that
taking an error model with a non-scalar covariance as we do here
allows us to consider model error (modeled by $\modcov$) as well as
observation error (modeled by $\sigma^2$). For example, say we believe
our forward model does not capture some small scale phenomenon.  Then
we may express this belief by saying $\tru = \fwd + \err$, with $\fwd$
depending on $\param$ and $\err$ depending on $\sspar$, with $\param
\perp \sspar$. We do not know much about this effect but it is
reasonable to assume it changes continuously in our domain. We (may
choose to) model it as $\normal (0, \modcov)$ and take $\modcov$ to
reflect the spatial (or other) variability we imagine $\err \sspar$
has. Such small scale phenomenon can arise as a modeling issue, where
we might not model the system in its entirety. It can also arise from
a numerical source, where our discretization of the system is not fine
enough to capture all small scale phenomena.
%%  In section \ref{section:non vanishing}, we will see that assuming
%% some correlation in the error mitigates the clusterization
%% phenomenon, as reported in the literature \cite{Ucinski05}.

@@

>>>>

\subsection{Overview}
In this section we will define notations that will be used throughout
the paper. Notations presented in the section are summarized in
Section \ref{subsec:notation}. The theoretical foundations for inverse
problems over function spaces can be found in \cite{Stuart10}.

@@

\subsubsection{Error Terms}
It is easy to verify that $\bar{\eps} := \obs \eps' + \eps \in \R^m$
is a centered Gaussian random vector with covariance
matrix

\begin{align}\label{eq:Sigma}
  \begin{split}
    \Sigma(\obs) :&= \mathbb{E}[ (\obs \eps' + \eps) (\obs \eps' +
      \eps)^t ]
    % 
    % 
    = \obs \modcov \obs^* + \sigma^2I , 
  \end{split}
\end{align}
where
\begin{equation}\label{eq:modcov explained}
  [\obs \modcov \obs^*]_{ij} = e_i^t \obs \modcov \obs^* e_j = \meas_i (\modcov \meas_j),
\end{equation}
and $e_j \in \R^m$ is the $j$th standard basis vector. The first
equality in \eqref{eq:modcov explained} holds by definition and the
second by \eqref{eq:obs*}. The explicit dependence on $\obs$ will be
mostly dropped for notational convenience, so $\Sigma(\obs) =
\Sigma$. Thus, for a fixed $\obs$ (i.e.\ a fixed set of observations)
we can equivalently write $\data = \obs \fwd \param + \bar{\eps}$ with
$\bar{\eps} \sim \normal(0,\Sigma)$. Taking $\modcov = 0$ is common
practice \cite{Tarantola05,Kaipio2006,Vogel02}. This reduces to the
case where we take iid observations. Then $\Sigma = \sigma^2I$ is
simply a scalar matrix that does not depend on $\obs$. Note that
taking an error model with a non-scalar covariance as we do here
allows us to consider model error (modeled by $\modcov$) as well as
observation error (modeled by $\sigma^2$). For example, say we believe
our forward model does not capture some small scale phenomenon.  Then
we may express this belief by saying $\tru = \fwd + \err$, with $\fwd$
depending on $\param$ and $\err$ depending on $\sspar$, with $\param
\perp \sspar$. We do not know much about this effect but it is
reasonable to assume it changes continuously in our domain. We (may
choose to) model it as $\normal (0, \modcov)$ and take $\modcov$ to
reflect the spatial (or other) variability we imagine $\err \sspar$
has. Such small scale phenomenon can arise as a modeling issue, where
we might not model the system in its entirety. It can also arise from
a numerical source, where our discretization of the system is not fine
enough to capture all small scale phenomena.
%%  In section \ref{section:non vanishing}, we will see that assuming
%% some correlation in the error mitigates the clusterization
%% phenomenon, as reported in the literature \cite{Ucinski05}.

@@

\subsection{Notation Summary}\label{subsec:notation}
  Our notation is summarized below. We let:
  \begin{itemize}
  \item $\hilp, \hilo$ Hilbert spaces.
  \item $\fwd:\hilp \to \hilo$ a linear compact operator.
  \item $\pr \sim \mathcal{N}(0, \prcov)$ prior Gaussian measure on
    $\hilp$, with prior covariance operator $\prcov:\hilp \to \hilp$.
  \item $\obs: \hilo \to \mathbb{R}^m$ observation operator, where $m
    \in \mathbb{N}$ is the number of observations taken. 
  \item $\sigma^2 \in \mathbb{R}_{+}$ observation noise variance.
  \item $\modcov$ model error covariance operator.
    %% $\data = \obs \fwd \param + \eps$, where $\eps \in
    %% \mathbb{R}^m$ isiid $\mathcal{N}(0, \sigma^2)$ noise.
  \item $\Sigma(\obs) = \obs \modcov \obs^* + \sigma^2I$. 
  \item $\post$ the posterior measure, with covariance $\postcov$.
  \item A D-optimality utility function
    \cite{AlexanderianGloorGhattas14}:
    \begin{align*}
      \begin{split}
        \tar(\obs) :&= \mathbb{E}_{\data}\left [ D_{\text{KL}} (\post || \pr ) \right ] \\
        % 
        % 
        % 
        &= \frac12 \log \det ( I + \prcov^{1/2} \fwd ^* \obs^* \Sigma(\obs)^{-1} \obs
        \fwd \prcov^{1/2}).
      \end{split}
    \end{align*}
  %% \item $\{\lambda_i\}_{i=1}^\infty$ eigenvalues of $\fwd\prcov\fwd^*$
  %%   in decreasing order of magnitude.
  %% %% \item $\{\ev_i\}_{i=1}^\infty$ their corresponding eigenvectors.
  %% \item $\{\eta_i\}_{i=1}^\infty$ eigenvalues of $\obs^*\obs$.
  \end{itemize}
